Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-01-23 article/figures.Rmd
+ fixed issues with order of bars in the violin plots + fixed issue with letters not showing in violin plots

```{r, echo=FALSE, fig.width=6, fig.height=3, fig.cap='Summary of single species prioritizations. Single species prioritizations were generated using amount-based targets, amount-based and surrogate-based targets, and amount-based and genetic-based targets for each species. Violin plots show the performance of prioritizations generated using these three sets of targets. Points denote the values associated with each prioritization. Letters denote significant differences ($P < 0.05$).'}
# prepare data for plotting
single.spp.PDF <- expand.grid(
	Prioritisation=unique(single.spp.SDF$Prioritisation),
	Metric=unique(single.spp.SDF$Metric)
) %>% mutate(
	letters=toupper(cld(single.spp.MCP)$mcletters$Letters),
	letter.height=max(single.spp.SDF$value)+(diff(range(single.spp.SDF$value))*0.1)
)
# make plot
ggplot(aes(x=Metric,y=value,fill=Prioritisation),
	data=single.spp.SDF) +
	geom_violin(position=position_dodge(0.9)) +
	geom_point(alpha=0.2,position=position_jitterdodge(dodge.width=0.9, jitter.width=0.25)) +
	geom_text(aes(x=Metric, y=letter.height, label=letters),
		data=single.spp.PDF, position=position_dodge(0.9)) +
	scale_fill_manual(name='Prioritisation',
		values=c('grey80','grey50','grey20')) +
	ylab('Genetic variation secured (%)') +
	xlab('') +
	theme_classic()
```

@@

```{r, echo=FALSE, fig.width=6, fig.height=3, fig.cap='Summary of multi-species prioritizations. Three prioritizations were generated using amount-based targets, amount-based and surrogate-based targets, and amount-based and genetic-based targets for each species. Data shows the performance of these prioritizations based on how much genetic variation they explain. See Figure 1 caption for conventions.'}
# prepare data for plotting
multi.spp.PDF <- expand.grid(
	Prioritisation=unique(multi.spp.SDF$Prioritisation),
	Metric=unique(multi.spp.SDF$Metric)
) %>% mutate(
	letters=toupper(cld(multi.spp.MCP)$mcletters$Letters),
	letter.height=max(multi.spp.SDF$value)+(diff(range(multi.spp.SDF$value))*0.1)
)
# make plot
ggplot(aes(x=Metric,y=value,fill=Prioritisation),
	data=multi.spp.SDF) +
	geom_violin(position=position_dodge(0.9)) +
	geom_point(alpha=0.2,position=position_jitterdodge(dodge.width=0.9, jitter.width=0.25)) +
	geom_text(aes(x=Metric, y=letter.height,label=letters),
		data=multi.spp.PDF, position=position_dodge(0.9)) +
	scale_fill_manual(name='Prioritisation',
		values=c('grey80','grey50','grey20')) +
	ylab('Genetic variation secured (%)') +
	xlab('') +
	theme_classic()
```

>>>>

```{r, echo=FALSE, fig.width=6, fig.height=3, fig.cap='Summary of single species prioritizations. Single species prioritizations were generated using amount-based targets, amount-based and surrogate-based targets, and amount-based and genetic-based targets for each species. Violin plots show the performance of prioritizations generated using these three sets of targets. Letters denote significant differences ($P < 0.05$).'}
# prepare data for plotting
single.spp.PDF <- expand.grid(
	Prioritisation=unique(single.spp.SDF$Prioritisation),
	Metric=unique(single.spp.SDF$Metric)
) %>% mutate(
	letters=toupper(cld(single.spp.MCP)$mcletters$Letters),
	letter.height=max(single.spp.SDF$value, na.rm=TRUE)+(diff(range(single.spp.SDF$value, na.rm=TRUE))*0.1)
)
# make plot
ggplot(aes(x=Metric,y=value,fill=Prioritisation),
	data=single.spp.SDF) +
	geom_violin(position=position_dodge(0.9)) +
	geom_text(aes(x=Metric, y=letter.height, label=letters),
		data=single.spp.PDF, position=position_dodge(0.9)) +
	scale_fill_manual(name='Prioritisation',
		values=c('grey80','grey50','grey20')) +
	ylab('Genetic variation secured (%)') +
	xlab('') +
	theme_classic()
```

@@

```{r, echo=FALSE, fig.width=6, fig.height=3, fig.cap='Summary of multi-species prioritizations. Three prioritizations were generated using amount-based targets, amount-based and surrogate-based targets, and amount-based and genetic-based targets for each species. Data shows the performance of these prioritizations based on how much genetic variation they explain. See Figure 1 caption for conventions.'}
# prepare data for plotting
multi.spp.PDF <- expand.grid(
	Prioritisation=unique(multi.spp.SDF$Prioritisation),
	Metric=unique(multi.spp.SDF$Metric)
) %>% mutate(
	letters=toupper(cld(multi.spp.MCP)$mcletters$Letters),
	letter.height=max(multi.spp.SDF$value, na.rm=TRUE)+(diff(range(multi.spp.SDF$value, na.rm=TRUE))*0.1)
)
# make plot
ggplot(aes(x=Metric,y=value,fill=Prioritisation),
	data=multi.spp.SDF) +
	geom_violin(position=position_dodge(0.9)) +
	geom_text(aes(x=Metric, y=letter.height,label=letters),
		data=multi.spp.PDF, position=position_dodge(0.9)) +
	scale_fill_manual(name='Prioritisation',
		values=c('grey80','grey50','grey20')) +
	ylab('Genetic variation secured (%)') +
	xlab('') +
	theme_classic()
```

### 2016-01-23 article/supporting_information.Rmd
+ fixed issues with order of bars in the violin plots + fixed issue with letters not showing in violin plots

```{r, echo=FALSE}
plot.spp.mds <- function(i) {
	# define function
	make.mds.plot <- function(j,k) {
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group', fill=paste0(unique(spp.samples.DF$species)[i], '_', j, '_d',k)),
				alpha=0.8, color='grey10') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(paste0(j,' (',k,')'))
	}
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	plotLST <- list()
	# make adaptive plot
	if (adapt.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['adaptive']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('adaptive', k)))
	} 
	# make neutral plot
	if (neutral.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['neutral']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('neutral', k)))
	}
	# make plot
	do.call(
		grid.arrange,
		append(
			plotLST,
			list(ncol=6)
		)
	)
}
```

>>>>

```{r, echo=FALSE}
plot.spp.mds <- function(i) {
	# define function
	make.mds.plot <- function(j,k) {
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group', fill=paste0(unique(spp.samples.DF$species)[i], '_', j, '_d',k)),
				alpha=0.8, color='grey10') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(paste0(j,' (',k,')'))
	}
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	plotLST <- list()
	# make adaptive plot
	if (adapt.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['adaptive']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('adaptive', k)))
	} 
	# make neutral plot
	if (neutral.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['neutral']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('neutral', k)))
	}
	# make plot
	do.call(
		grid.arrange,
		append(
			plotLST,
			list(ncol=4)
		)
	)
}
```
